A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-10-02 manuscript.Rmd
terminal -> comand line in code chunks closes #71

```{bash, eval=FALSE}
# -- type this in a terminal --
git init # to initialize Git in the current directory
git add ./data/iris.csv ./R/analysis.R # track specific files
git commit -m "added data and analysis" # take snapshot with comment
# once script or data were changed, take a new snapshot
git commit -a -m "completed data collection" # add and commit all changes
```

@@

```{bash, eval = FALSE}
# -- type this in a terminal --

@@

```{bash, eval=FALSE}
# -- type this in a terminal --

@@

```{bash, eval=FALSE}
# -- type this in a terminal --
git clone https://github.com/aaronpeikert/reproducible-research.git
```

>>>>

```{bash, eval=FALSE}
# -- type this on the command line --

git init # to initialize Git in the current directory
git add ./data/iris.csv ./R/analysis.R # track specific files
git commit -m "added data and analysis" # take snapshot with comment
# once script or data were changed, take a new snapshot
git commit -a -m "completed data collection" # add and commit all changes
```

@@

```{bash, eval = FALSE}
# -- type this on the command line --

@@

```{bash, eval=FALSE}
# -- type this on the command line --

@@

```{bash, eval=FALSE}
# -- type this on the command line --

git clone https://github.com/aaronpeikert/reproducible-research.git
```
